Spillover Effects of Information and Communication Technology on Future TFP using a Structural VAR Approach

### 2018-05-31 Latex/Slides_for_Final_Draft_June_2018/Slides_June2018.tex
Starting final slides draft

\title{IT Spillovers in Long-Run TFP \\ A SVAR Approach}

\date{April 26, 2018}

@@

@@

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Shocks}

\begin{equation}\label{eq:prodfuncfinal}
y_{c,t} = N_t  \  \ \Gamma_{c,t}  \  \ k_{i,t}^{\gamma} \ \  h_{1,t}^{1 - a- b} k_{c,1,t}^a k_{i,1,t}^b
\end{equation}

\begin{equation}\label{eq:prodfuncinter}
y_{i,t} = N_t \ \ \Gamma_{i,t} \ \ k_{i,t}^{\gamma} \ \  h_{2,t}^{1 - a- b} k_{c,2,t}^a k_{i,2,t}^b
\end{equation}

The uses of the outputs are
$$
y_{c,t} = c_t + i_{c,t} \ \ \text{and} \ \ y_{i,t} = i_{i,t}
$$

\begin{itemize}
\item News shock is $\varepsilon$, $N_{t} = \rho_N N_{t-1} + \varepsilon_{t-k}$
\item Noise shock (contemporaneous) is $\eta$, $E_t \Gamma_{i,t} = \Gamma_{i,t} + \eta_t$
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{TFP response to both shocks}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_TFP__} % REGENERATE TFP SHOCKS FIGURES WITH RIGHT SCALES!!
\end{figure}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_TFP__}
\end{figure}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{IT investment response to both shocks}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_IT_Investment__}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_IT_Investment__}
\end{figure}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\title{Spillover Effects of Information and Communication Technology on Future TFP using a Structural VAR Approach}

\date{June 2018}

@@

		\item Literature agrees on the importance of Total Factor Productivity (TFP) in driving long-run economic performance.

		\item However, less agreement on the underlying driver of TFP.

@@

@@

@@
